Modelling the City of Melbourne Pedestrian Data

### 2017-05-06 presentation/proposal_pres.Rmd
slides update

```{r setup, include=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE)
library(readr)
library(dplyr)
library(ggplot2)
library(ggmap)
library(knitr)
library(pander)
library(lubridate)
  ped_df <- read_csv("../data/Pedestrian_volume__updated_monthly_.csv")

@@

---
class: center, inverse

@@

The project has been split into multiple steps:  
  - Data Cleaning
  - Modelling
  - Visualisation
  - Shiny app development

@@

While the data variables themselves are relatively tidy, there is a large number of observations we need to impute

>>>>

```{r setup, include=FALSE, echo = FALSE, warning=FALSE, message=FALSE}
options(htmltools.dir.version = FALSE, scipen = 100)
library(readr)
library(dplyr)
library(ggplot2)
library(ggmap)
library(knitr)
library(pander)
library(lubridate)
  ped_df <- read_csv("../data/Pedestrian_volume__updated_monthly_.csv")

@@

---
class: inverse

@@

### The project has been split into multiple steps:

  - Data Cleaning
  - Modelling
  - Visualisation
  - Shiny app development

@@

### While the data variables themselves are relatively tidy, there is a large number of observations we need to impute:
